---
title: "Happiest Countries in the World"
author: "Press page down/up to navigate slides"
date: "5/4/2022"
output: ioslides_presentation
---
```{r libraries,echo=FALSE,message=FALSE,warning=FALSE}
library(plotly)
library(tidyverse)
```


## Happiest Countries over Time

This presentation uses data collected from the Gallup World Poll and contains information
about many countries around the world. It includes information on their happiness, 
GDP per capita, and a number of other predictors.

I will be focused on how happiness changes in the happiest countries over a certain
time period.

## Variables of Interest in the Dataset

- Life Ladder: A measure of percieved happiness with possible scores ranging from 1-8
- GDP per Capita: Provides an index of the economic output of a nation per person
- Healthy life Expectancy at Birth: Expected life expectancy for a given year

## Read in the dataset

```{r happydata, echo = TRUE}
data<-read.csv("world-happiness-report.csv")
colnames(data)[1]<-"Country"
data<-na.omit(data)
```

```{r happiest countries}
happycountry<-data%>%
    group_by(Country)%>%
    summarise(avghappy=mean(Life.Ladder))%>%
    arrange(desc(avghappy))
happiest<-happycountry[1:5,]
happydat<-data[data$Country%in%happiest$Country,]
happydat
```
## Happiness across the years
```{r pressure, echo=FALSE}
happydat%>%plot_ly(y=~Life.Ladder,x=~year,color=~Country)%>%
    add_lines()
```

