---
title: "Happiest Countries in the World"
author: "Press page down/up to navigate slides"
date: "5/5/2022"
output: ioslides_presentation
---
```{r libraries,echo=FALSE,message=FALSE,warning=FALSE}
library(plotly)
library(tidyverse)
```


## Happiest Countries over Time

This presentation uses data collected from the Gallup World Poll and contains information
about many countries around the world. It includes information on their happiness, 
GDP per capita, and a number of other predictors.

I will be focused on how happiness changes in the happiest countries over a certain
time period.

## Read in and prepare the dataset

```{r happydata, echo = TRUE}
data<-read.csv("world-happiness-report.csv")
colnames(data)[1:3]<-c("Country","Year","Happiness")
data<-na.omit(data)
```

Selecting the 5 happiest countries on average

```{r happiest countries}
happycountry<-data%>%
    group_by(Country)%>%
    summarise(avghappy=mean(Happiness))%>%
    arrange(desc(avghappy))
happiest<-happycountry[1:5,]
happydat<-data[data$Country%in%happiest$Country,]
```

## Happiness in 5 Happiest Countries from 2006-2020
```{r pressure, echo=FALSE}
happlot<-ggplot(happydat,aes(x=Year,y=Happiness,color=Country))+
    geom_line()
ggplotly(happlot)
```

